### 2022-09-17 docs/Ideas.rmd
m

Parece que hay una tendencia a buscar clases on line, ademas las universidades estan experimentando bajos enrollments.
Factores socio-enconimicos? mas tiempo para trabajar? correlacion con la inflacion? 
Otras carreras como economia, ingieneria no han tenido una bajada en el numero de solicitudes. Hay un cambio de tendencia en lo que se estudia?.

Preguntas para añadir,

Open questions, such as are you currently working? If so how many hours? Is your job related with your minor/ major?

Do students see language as a useful factor to find a job? 
“ Computer sciences increased by 7.8%, visual and performing arts majors were up 5.7% and psychology majors increased 4%. 
The largest declines among the most popular majors were in liberal arts and sciences, general studies and humanities (-4.2%) and social sciences (-2.3%).”
https://www.forbes.com/sites/michaeltnietzel/2022/05/26/new-report-the-college-enrollment-decline-has-worsened-this-spring/?sh=66eff6ef24e0

### 2022-09-17 docs/Ideas.rmd
m

@@
+# Percepciones 
 Parece que hay una tendencia a buscar clases on line, ademas las universidades estan experimentando bajos enrollments.
@@
 
-Preguntas para añadir,
+# Tipo de preguntas. Number of agreement / describir- open questions
 
 Open questions, such as are you currently working? If so how many hours? Is your job related with your minor/ major?
+
+Do you consider you need to work to cover your university expenses?
 
@@
 The largest declines among the most popular majors were in liberal arts and sciences, general studies and humanities (-4.2%) and social sciences (-2.3%).”
+
 https://www.forbes.com/sites/michaeltnietzel/2022/05/26/new-report-the-college-enrollment-decline-has-worsened-this-spring/?sh=66eff6ef24e0
+
+# Background
+
+Have you taken language online class during the pandemic? If so how many?
+
+Have you taken a f2f class after schools started offering them again?
+
+Do you have a preference for online class? Advantages/Disadvantages

### 2022-09-17 docs/Ideas.rmd
m

@@
 # Percepciones 
-Parece que hay una tendencia a buscar clases on line, ademas las universidades estan experimentando bajos enrollments.
-Factores socio-enconimicos? mas tiempo para trabajar? correlacion con la inflacion? 
+Parece que hay una tendencia a buscar clases on line, -- las universidades estan experimentando bajos enrollments.
+**Cual puede ser la razon de la tendencia al online** Factores socio-enconimicos? mas tiempo para trabajar? correlación con la inflacion? 
 Otras carreras como economia, ingieneria no han tenido una bajada en el numero de solicitudes. Hay un cambio de tendencia en lo que se estudia?.

### 2022-10-26 docs/draft/info_damaris.Rmd
info damaris

---
title: "Information from Language Program Qualtrics Survey"
output: pdf_document
author: Nicole Rodríguez
---

# Number and profile of participants

A total number of 87 people responded, I took out the data from 6 surveys because they didn't respond to every question and/or just clicked through to try to gain extra credit. The students all fall in the traditional student age range of 18-25, except for 1 that falls in the 25-35 age range.

Here is a breakdown of the courses that the students are currently taking:

| Course number | Number of students |
|:--------------|:-------------------|
| 940:101:01    | 1                  |
| 940:101:94    | 3                  |
| 940:102:90    | 1                  |
| 940:121:01    | 13                 |
| 940:121:02    | 1                  |
| 940:131:01    | 12                 |
| 940:131:02    | 1                  |
| 940:131:03    | 14                 |
| 940:131:90    | 2                  |
| 940:132:01    | 9                  |
| 940:132:90    | 13                 |
| 940:132:91    | 4                  |
| 940:261:01    | 7                  |

The divide between online vs in person students who completed the survey is 23 online, 51 online, and 7 hybrid. There are 35 Freshmen, 27 Sophomores, 11 Juniors, and 9 seniors. Before COVID, only 9 students had taken online courses, whereas 73 had not.

The students speak other languages at home, we have Mandarin, Hindi (6), Gujarati (5), Kannada, Korean (2), Malayalam (2), Haitian Creole, Telugu (3), Arabic, Tamil (5), Urdu (3), Bengali (2), Romanian, Armenian, Turkish, Portuguese, and Japanese speakers taking Spanish courses.

We have a mix of commuters and students who live on-campus (1-5 miles away) or close to campus (5-15 miles away) and students who live quite far (15-20+ miles away):

| Distance         | Number of students |
|:-----------------|:-------------------|
| 1-5 miles away   | 32                 |
| 5-10 miles away  | 5                  |
| 10-15 miles away | 12                 |
| 16-20 miles away | 6                  |
| 20+ miles away   | 27                 |

This is something we should take into consideration as it will likely play a role in if they are choosing online or in person classes.

We also have students who are working (31 total vs 51 who are not currently working). Of those 31 students who are working, 5 work between 0-5 hours a week, 10 work between 5-10 hours a week, 10 work between 10-15 hours a week, 3 work between 15-20 hours, and 3 work 20+ hours a week. This is another thing we should take into consideration, especially when it comes to providing sections of online classes.

# Motivation for taking a language course

The students were asked to describe their motivation for taking language courses in an open-ended response question. I made a word cloud that visualizes common themes in their answers.

![](../imgs/wordcloud.png)

Unfortunately, the vast majority of people are taking Spanish courses to fill a requirement for the Honors College, SAS, or their major or minors. I'm not sure if this is good or bad news... as it seems like the Honors College students are very vocal about only being there because they need to fill a requirement (32 students). There are quite a few people here learning Spanish because their partner's families speak Spanish. More than 8 students mentioned it would be beneficial for their future careers (either in Health Care or Law). We should consider offering or developing more Spanish for the professions courses for these students. Then we have the students that we love to see in the department that mention fostering deeper connections and being able to communicate with others in a common language.

# Motivation for choosing in person or online

The people who responded with why they chose an in person class all had similar answers. Here are the ones that stick out the most.

- "I feel like with learning a language, the in person communication is super important. One of the best ways of learning a language is by surrounding yourself by people that can also speak the language well. Online would have taken some of this away from the opportunity."

- "I knew that face-to-face interaction would force me to pay attention and not get distracted."

- "So I can build a professional relationship with my professor and get more help"

- "In person is much easier to learn a language because you can have more fluid and consistent conversations."

- "I felt that an in person class would be better for me in terms of my learning and comprehension of the language. I also believe that an online class would make me lazy and I wouldn't do as much as work as if I did in person class."

- "I think with an in-person class I can learn a lot more. Having a face-to-face conversation with my professor in Spanish is more valuable than one with my computer screen. I can say this with experience because I took an online class during the Spring semester of 2022."

The majority of the students who answered this question focused on the benefits of face-to-face interactions with peers and the instructor. But, there responses along the lines of "this was the only section open" or "I didn't know online classes were available".

For the students who chose online instead, here are some of the answers that stick out:

- "I choose an online class over an in person class because it offers me more flexibility on when to complete the tasks assigned."

- "In-person classes don't work for my schedule."

- "I chose an online class because the time for the in person class could not work into my schedule. However, an online class allows me to work and study on my own pace while abiding by the deadlines."

There were unfortunately answers like the following:

- "I didn't choose because it was an online, but I realized it was the only available language course that would work with my schedule."

- "I have never liked taking spanish, so taking it online allowed me to avoid the pain of taking it in person."

I think in general, our students who are commuters or who work full-time hours are taking advantage of the online classes because they fit better with their work schedule. This is further confirmed when they answered the question "Do online classes facilitate having a job with attending Rutgers?" and 57.32%	(47 students) said yes. But overall, I believe students prefer in person language classes. To see how effective they find online classes we asked: "On a scale of 1 to 5, how effective do you believe online language education is (in comparison to face-to-face or hybrid)? 1 = not effective at all and 5 = very effective" Here is a breakdown of their responses:

| Scale response           | Number of responses |
|:-------------------------|:--------------------|
| 1 = not effective at all | 7                   |
| 2                        | 16                  |
| 3                        | 33                  |
| 4                        | 22                  |
| 5 = very effective       | 3                   |

In general, it appears that they don't have a preference towards one format or the other, with the majority of the responses falling in the 3 range. But it should be noted that staying motivated in a class is more likely to happen in a face-to-face class vs an online one. This can be seen below as the majority (67 responses) favored face-to-face classes for staying motivated than online ones:

![](../imgs/motivation.png)

# How we're doing

Overall, I think we're doing well. When asked if they thought that they have progressed in their language abilities thus far (at the midpoint in the semester), the vast majority said yes (77 students).

![](../imgs/progress.png)

The students that responded with "No" to that question listed the follow reasons as to why they have not made any progress:

- "Because I took online classes"

- "I keep getting discouraged when I do not get something everyone seems to know"

- "Instruction isn't very in depth, class feels rushed" (this student comes from 940:121:01)

- "It's my fault, I have not allotted the proper amount of time to it"

There are three things we could take from this to work on for the future. The first, we should take a look at our asynchronous online classes and see what improvements can be made to them. Maybe reformatting the assignments or the way that they are set up would be beneficial.

The second, we should offer for next semester a "best practices" PD for the TAs next semester, so we can get at "in depth instruction in the language classroom". Or something focused on comprehension checking so that the students who are feeling lost or that instruction isn't very in depth will have their needs met.

The third, is not necessarily something we can do, but something that we should add to the syllabus that mentions putting in the time and work, as learning a language is difficult and a journey that doesn't necessarily have a destination. Students should be made aware that learning a language (especially Spanish) will not be an easy A and it is a course just like in another other discipline that requires work, attention, and effort.

The students were asked how much practice they have had in the target language in speaking, reading, writing, and listening on a scale of 1 to 5 where 1 is no practice at all and 5 is a lot of practice. Here is a visualization of their answers:

![](../imgs/practice.png)

The colors refer to the following skills: red is speaking practice, purple is reading practice, blue is writing practice, and green is listening practice. Overall, it appears that students are getting sufficient practice in each area of language learning/use, but let's take a deeper look at their responses.

The students were asked the follow-up question of "why they felt they haven't had enough practice in speaking, reading, writing, or listening?" and here are the responses that stick out:

- We do not receive as many listening assignments compared to others (Student from 940:132:91)

- Since the course is online, I don't have enough opportunities to have real conversations with others.

- It was not covered as much or practiced as much in writing specifically.

- Recording is different than actually communicating with other people. (Student from 940:132:91)

- The work is not appealing (Student from 940:131:01)

- I feel like for listening, it takes me a lot of time to break down the sentences to a level where I can understand. It is difficult for me to practice because I'm not exposed to Spanish on a daily level, and even when I listen to Spanish music, the speaking speed is too fast for me. Speaking and writing is easier for me because I can see it right in front of me. Reading is somewhere in the middle, where I can understand the general subject or question of the sentence, but I may not know all the meaning of the words.

- It is really just comes down to time management. On top of other classes I have work and other obligations. I try to practice as much as I can but I cannot always get the amount of practice I would like

- We don't read, speak, or write in spanish very often in class (Student from 940:121:01)

- We don't do many activities for writing or speaking (Student from 940:121:01)

- I feel like I need more practice in speaking because it's the hardest part of learning a language for me. Not only do you have to use the correct grammar and pronunciation but you also have to think on the spot which stresses me out and makes me forget what I wanted to say (Student from 940:131:01)

- I don't think there's been enough speaking practice (Student from 940:132:90)

I think there is a lot to unpack here that could be a good starting point to a discussion on what/where improvements can be made so that students in all classes, no matter the format, are getting adequate practice in all areas. The biggest thing right now that I'm seeing, and something we should try to find a solution for, is having assignments, practice, or a system/resource in place for online students to get the speaking practice and interactions with other speakers that they are craving. For the other comments, I think we could come up with solutions, ideas, and other improvements for the language program for either next semester or the following year. Overall, students are progressing in their language abilities, but there is always room for improvement :)

### 2022-10-26 scripts/00_libraries.R

@@ -1,0 +1,24 @@
+# Load libraries ----------------------------------------------------
+
+library("dplyr")
+library("tidyr")
+library("readr")
+library("here")
+library("glue")
+library("ggplot2")
+library("ggbeeswarm")
+library("forcats")
+library("fs")
+library("purrr")
+library("patchwork")
+library("psycho")
+library("stringr")
+library("polypoly")
+library("corrplot")
+library("ggdist")
+library("flextable")
+library("knitr")
+library("wordcloud")
+library("RColorBrewer")
+
+# -----------------------------------------------------------------------------

### 2022-10-26 scripts/02_tidy_survey.R

@@ -1,0 +1,11 @@
+# Source libraries  -----------------------------------------------------------
+
+source(here::here("scripts", "00_libraries.R"))
+
+# -----------------------------------------------------------------------------
+
+
+# Tidy survey data ------------------------------------------------------------
+# Data from Qualtrics 10/21 ---------------------------------------------------
+
+survey_raw %>% read.csv("data", "raw", "language_program_survey102122.csv")

### 2022-11-03 docs/draft/draft.Rmd
start of draft

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

# Introduction

** big picture = social implications of online teaching and how that has changed in a post-pandemic world
** small picture = what we are doing in this language program and how can we improve to meet the needs and wants of the students in their new reality

- Address the general idea

- Explain the study

- Address our contribution

# Literature Review

- Look at format of the other papers that we have saved in this repo

# Current Study

Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. 
The effects of this ever-changing learning environment have affected students and continue to affect modulating the way they interact with and view their education. Post-pandemic effects, along with world socio-economic changes, have brought a new educational reality that affects tendencies toward enrollment. 
Having a better understanding of the constant change of tendencies that affect our students can help us not only in providing them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.

# Methods

## RQs

The current study aims to answer the following research questions:

- How effective are online classes according to self-reported measures of language abilities?

- How does our new post-pandemic reality modulate tendencies in language enrollment (in person vs online)?

We predict X based on Y.

In order to answer the research questions, a total of X students completed an anonymous survey. The following is a description of the participants that took part in the study and the task that they completed.

## Participants

Students who were taking in person and online Spanish language classes at a Big 10 northeastern university were asked to complete the survey. 
A total number of 87 people responded (update this with final count from Qualtrics). 
The data from 6 surveys were removed due to incomplete responses. 
The participants were compensated with extra credit towards their homework grades in their Spanish courses for completing the survey. 
They were all typical university aged students (ages from 18-25) except one student, who belongs to the 25-35 age range. 
[I don't know if this will be relevant, probably not, but we could include: 35 of the students were first years, 27 were second years, 11 were third years, and 9 were fourth years.] 
Of the # participants who completed the survey, 23 were taking a fully asynchronous online Spanish class, 51 were taking an in person class, and 7 were taking a hybrid course.

We also collected information about their linguistic backgrounds. 
Of the # of participants, 37 of the students speak another language besides English and Spanish. 
The participants reported learning Spanish between the ages of X and X. 
They had reported learning Spanish in X setting. 
X number of participants had taken X number of years of Spanish in a high school setting. 
X students have never taken Spanish courses prior to this course. (look up this information in the survey)

Additionally, we collected information about their work and commuting lives of these participants to be able to make judgements about how these factors impact learning attitudes. 
The students ranged from living on campus (32 students) to living relatively close to campus 5-15 miles away (17 students), to living 15+ miles away from campus and having a long commute (33 students). 
As for their working schedules, 51 students reported to not be currently working while attending university while 31 students are currently studying and working at the same time. 
Of those 31 students who are working, five work between zero and five hours a week, ten work between five to ten hours a week, ten work between ten to fifteen hours and week and six work more than fifteen hours a week.

## Material and Procedure

The survey was created on Qualtrics. 
It was distributed via an online anonymous link to undergraduate students taking Spanish courses in a large university located in the northeast United States and it took an average of # minutes to complete (find this info on qualtrics). 
In total, the participants answered 46 questions. 
The questions were divided into 4 sections (background information, online learning tools/accessibility, attitudes, and enrollment) that each aimed to gather information about different factors that might impact the responses. 
The background information section asked questions about their age, how long they have studied Spanish, how far they live away from campus, and if they are working. 
The online learning tools/accessibility questions asked how comfortable they felt using the learning management systems that their courses are using and how readily accessible stable Wifi, a computer or tablet, and the software and other technologies are that are required for the courses that they are taking. 
The attitudes section aimed to gather the participants' thoughts about learning languages in person and in online settings, their motivations for taking a language course, and how they feel their language abilities have progressed. 
The last section, enrollment, asked questions about school-work balance and the reasons why they enroll in online courses.

The aforementioned sections of the survey followed a mixed-methods design to examine students’ perspectives through an interaction of quantitative and qualitative questions.
By using open-ended and close-ended questionnaires we were able to collect, contrast and students’ testimonies. 
The mixed-methods design of this study allowed us to compare open-ended questions, with close-ended questions obtaining tendencies, preferences, as well as attitudes toward enrollment. 
Close-ended quantitative questions were presented in a scale from 5 to 1 in the questionnaire, with a 5 being valued as “very useful” and a 1 as “not very useful”.

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

- Tie to RQs and big picture

# Conclusion

- Big Picture

- Limitations

- Future directions

The results of this research study can help inform the decisions that administrations at similar universities make about the courses that they offer in the future.

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2022-11-03 scripts/02_tidy_survey.R

@@ -8,4 +8,73 @@ source(here::here("scripts", "00_libraries.R"))
 # Tidy survey data ------------------------------------------------------------
 # Data from Qualtrics 10/21 ---------------------------------------------------
 
-survey_raw %>% read.csv("data", "raw", "language_program_survey102122.csv")
+tidy_data <- read.csv("data/tidy/tidy_survey_partial.csv")
+
+
+# Me messing around and trying graphs / stats stuff so don't take this seriously
+# Lets do a general descriptive stuff on this to find out information
+
+# finding # of participants
+
+# find # of participants per group
+n_participant <- tidy_data$responseid %>%  unique() %>%  length() %>% View
+n_trials <- tidy_data %>% nrow()
+# total = 91 participants
+
+# find # of participants by class format
+tidy_data %>%
+  group_by(class_format) %>%
+  summarize(., totals = n_distinct(responseid)) %>%  View
+
+# f = 58
+# h = 8
+# o = 30
+
+# find out their year/promoción
+
+tidy_data %>%
+  group_by(year) %>%
+  summarize(., totals = n_distinct(responseid)) %>%  View
+
+# 1 = 40
+# 2 = 28
+# 3 = 13
+# 4 = 10
+
+
+# okay so lets look at enrollment ~ progress
+tidy_data %>%
+  group_by(class_format) %>%
+  summarize(progress) %>%
+  ggplot(., aes(x = class_format, y = progress)) +
+  geom_point()
+
+# ^ that needs to be changed but i'm too lazy to do it right now
+
+# then you want to look at progress overall etc
+
+tidy_data %>%
+  group_by(progress) %>%
+  summarize(., totals = n_distinct(responseid)) %>%  View
+
+# No 5
+# Yes 82
+# we can say something like the majority said that they progressed in their language skills
+# then we can go into practice amount as a function of format (actually
+# you should double check that w/ dependent and independent variables)
+
+# then you want to look at enrollment based on anxiety, work, and commute
+# whatever code you do for above, is going to be the same thing here just with different variables
+
+# say something about online pre covid
+tidy_data %>%
+  group_by(online_pre) %>%
+  summarize(., totals = n_distinct(responseid)) %>%  View
+
+# No 81
+# Yes 9
+# Before COVID, the vast majority of the people had never taken an online class, so if we look
+# at the format of their classes now (figure this out) so we can say, people who have taken
+# online classes before covid either stick to online or go back to in person
+
+

### 2022-11-05 docs/draft/draft.Rmd
Update draft.Rmd

@@
 # Literature Review
+
+Big picture: 
+-	Pre pandemic  
+ In 2018, the percentage surpassed 35% according to the US Department of Education (2019). – no more than 2/3 lines.
+
+-	During pandemic 
+ “ In fall 2020, some 75 percent (11.8 million) of all undergraduate students were enrolled in at least one distance education course, and 44 percent (7.0 million) of all undergraduate students exclusively took distance education courses.
+The number of undergraduate students enrolled in at least one distance education course was 97 percent higher in 2020 than prior to the pandemic in fall 2019 (11.8 million vs.
+6.0 million).
+The number of undergraduate students exclusively enrolled in distance education courses was 186 percent higher in 2020 than in 2019 (7.0 million vs.
+2.4 million).”.
+US department of education (2022) – es un copy paste-  hay que ver que nos interesa.
+https://nces.ed.gov/fastfacts/display.asp?id=80 
+https://nces.ed.gov/programs/coe/indicator/cha/undergrad-enrollment
+
+Several studies have analyzed online vs f2f.  general tendency says XX
+Sangmin-Michelle (2020) students perceive online education as less effective
+Ruiz-Aloson-Bartol et all (2022) Students had the belief that learnt less that what they could have learnt in a traditional face to face class.
+Este paper cita bastantes estudios viejos donde encuentran que la educación online tiene ventajas.
+Son todo papers pre-pandemic.
+
+Interesante 
+“7 out of 10 feel the online instruction they received this Winter is worse than in-person instruction
+https://tophat.com/press-releases/adrift-in-a-pandemic-survey/
+
+-	Post pandemic
+
+ autonomy, effectiveness of instruction, engagement, interactivity, and openmindedness statistically significant effects were observedPusey and Alexander (2022)- online and effectiveness of instruction
+
+- see a way to link with our study. Which paper is the most similar to ours?
 

### 2022-11-05 docs/draft/draft.Rmd
Update draft.Rmd

@@
  “ In fall 2020, some 75 percent (11.8 million) of all undergraduate students were enrolled in at least one distance education course, and 44 percent (7.0 million) of all undergraduate students exclusively took distance education courses.
-The number of undergraduate students enrolled in at least one distance education course was 97 percent higher in 2020 than prior to the pandemic in fall 2019 (11.8 million vs.
-6.0 million).
-The number of undergraduate students exclusively enrolled in distance education courses was 186 percent higher in 2020 than in 2019 (7.0 million vs.
-2.4 million).”.
+The number of undergraduate students enrolled in at least one distance education course was 97 percent higher in 2020 than prior to the pandemic in fall 2019 (11.8 million vs. 6.0 million). 
+The number of undergraduate students exclusively enrolled in distance education courses was 186 percent higher in 2020 than in 2019 (7.0 million vs. 2.4 million).”.
 US department of education (2022) – es un copy paste-  hay que ver que nos interesa. 
@@
 Several studies have analyzed online vs f2f.  general tendency says XX
-Sangmin-Michelle (2020) students perceive online education as less effective
+Sangmin-Michelle (2020) students perceive online education as less effective, 
+Alhamami (2022) found a more positive attitude toward face-to-face enviroments in comparison to online class. 
 Ruiz-Aloson-Bartol et all (2022) Students had the belief that learnt less that what they could have learnt in a traditional face to face class.

### 2022-11-07 scripts/00_libraries.R
bibtext file

@@ -20,5 +20,9 @@ library("flextable")
 library("knitr")
 library("wordcloud")
 library("RColorBrewer")
+library("foreign")
+library("MASS")
+library("Hmisc")
+library("reshape2")
 
 # -----------------------------------------------------------------------------

### 2022-11-07 scripts/02_tidy_survey.R

@@ -8,7 +8,8 @@ source(here::here("scripts", "00_libraries.R"))
 # Tidy survey data ------------------------------------------------------------
 # Data from Qualtrics 10/21 ---------------------------------------------------
 
-tidy_data <- read.csv("data/tidy/tidy_survey_partial.csv")
+tidy_data <- read.csv("data/tidy/tidy_survey_partial.csv") %>%
+
 
 
 # Me messing around and trying graphs / stats stuff so don't take this seriously
@@ -42,14 +43,14 @@ tidy_data %>%
 # 4 = 10
 
 
-# okay so lets look at enrollment ~ progress
+# okay so lets look at practice_rate ~ practice type
 tidy_data %>%
-  group_by(class_format) %>%
-  summarize(progress) %>%
-  ggplot(., aes(x = class_format, y = progress)) +
-  geom_point()
+  ggplot(., aes(x = class_format, y = practicerate)) +
+  geom_boxplot(size = .75) +
+  geom_jitter(alpha = .5) +
+  facet_grid("practice")
 
-# ^ that needs to be changed but i'm too lazy to do it right now
+# ^ that needs to be made prettier
 
 # then you want to look at progress overall etc
 
@@ -62,9 +63,29 @@ tidy_data %>%
 # we can say something like the majority said that they progressed in their language skills
 # then we can go into practice amount as a function of format (actually
 # you should double check that w/ dependent and independent variables)
+# actually i think we need to do an ordinal regression
+
+
+
+practice_stats <- polr(practicerate ~ class_format, data = tidy_data)
+
+practice_stats <- lm(practicerate ~ effective, data = tidy_data)
+summary(practice_stats)
+
+practice_stats1 <- lm(practicerate ~ effective + class_format, data = tidy_data)
+summary(practice_stats1)
+
+practice_stats2 <- lm(practicerate ~ effective + class_format + practice, data = tidy_data)
+summary(practice_stats2)
 
 # then you want to look at enrollment based on anxiety, work, and commute
 # whatever code you do for above, is going to be the same thing here just with different variables
+
+enrollment_stats <- lm(practicerate ~ effective + class_format + work_hours, data = tidy_data)
+summary(enrollment_stats)
+
+enrollment_stats1 <- lm(practicerate ~ effective + class_format + work_hours + commute, data = tidy_data)
+summary(enrollment_stats1)
 
 # say something about online pre covid
 tidy_data %>%
@@ -73,6 +94,7 @@ tidy_data %>%
 
 # No 81
 # Yes 9
+
[…]

### 2022-11-08 scripts/02_tidy_survey.R
math?

@@ -8,7 +8,7 @@ source(here::here("scripts", "00_libraries.R"))
 # Tidy survey data ------------------------------------------------------------
 # Data from Qualtrics 10/21 ---------------------------------------------------
 
-tidy_data <- read.csv("data/tidy/tidy_survey_partial.csv") %>%
+tidy_data <- read.csv("data/tidy/tidy_survey_partial.csv")
 
 
 
@@ -67,25 +67,38 @@ tidy_data %>%
 
 
 
-practice_stats <- polr(practicerate ~ class_format, data = tidy_data)
-
-practice_stats <- lm(practicerate ~ effective, data = tidy_data)
+practice_stats <- polr(as.factor(class_format) ~ practicerate, data = tidy_data, Hess = TRUE, method = c("logistic"))
 summary(practice_stats)
 
-practice_stats1 <- lm(practicerate ~ effective + class_format, data = tidy_data)
+practice_stats1 <- polr(as.factor(class_format) ~ practicerate + practice, data = tidy_data, Hess = TRUE, method = c("logistic"))
 summary(practice_stats1)
 
-practice_stats2 <- lm(practicerate ~ effective + class_format + practice, data = tidy_data)
+practice_stats2 <- polr(as.factor(class_format) ~ practicerate + practice + progress, data = tidy_data, Hess = TRUE, method = c("logistic"))
 summary(practice_stats2)
+
+## It seems like nothing is interesting here, which we could make the argument that they're learning
+## just as well in both formats, so thats cool.
 
 # then you want to look at enrollment based on anxiety, work, and commute
 # whatever code you do for above, is going to be the same thing here just with different variables
 
-enrollment_stats <- lm(practicerate ~ effective + class_format + work_hours, data = tidy_data)
+enrollment_stats <- polr(as.factor(class_format) ~ work, data = tidy_data, Hess = TRUE, method = c("logistic"))
 summary(enrollment_stats)
 
-enrollment_stats1 <- lm(practicerate ~ effective + class_format + work_hours + commute, data = tidy_data)
+enrollment_stats1 <- polr(as.factor(class_format) ~ work + work_hours, data = tidy_data, Hess = TRUE, method = c("logistic"))
 summary(enrollment_stats1)
+
+enrollment_stats2 <- polr(as.factor(class_format) ~ work + work_hours + commute, data = tidy_data, Hess = TRUE, method = c("logistic"))
[…]

### 2022-11-09 scripts/02_tidy_survey.R
update

@@ -60,6 +60,8 @@ tidy_data %>%
 
 # No 5
 # Yes 82
+
+
 # we can say something like the majority said that they progressed in their language skills
 # then we can go into practice amount as a function of format (actually
 # you should double check that w/ dependent and independent variables)

### 2022-11-10 scripts/03_stats_writeup.Rmd
i hate math

---
title: "Language Program Qualtrics Survey"
output: pdf_document
---

```{r, load-libraries, echo=F}

source(here::here("scripts", "00_libraries.R"))

tidy_data <- read.csv("data/tidy/tidy_survey_partial.csv")

```

Okay so I'm going to write this as if we were going to use it in the paper. 
Hopefully that helps us.

# Results

## Descriptive statistics

```{r, descriptive, echo=T}

# finding # of participants

# find # of participants per group
n_participant <- tidy_data$responseid %>%  unique() %>%  length() %>% View
n_trials <- tidy_data %>% nrow()
# total = 91 participants

# find # of participants by class format
tidy_data %>%
  group_by(class_format) %>%
  summarize(., totals = n_distinct(responseid)) %>%  View

# f = 58
# h = 8
# o = 30

# find out their year/promoción

tidy_data %>%
  group_by(year) %>%
  summarize(., totals = n_distinct(responseid)) %>%  View

# 1 = 40
# 2 = 28
# 3 = 13
# 4 = 10

```
A total number of 102 participants completed the survey. 
After initial data cleaning to filter through participants who did not complete the survey, 91 participants were included in the analysis. 
Of those 91 participants, 58 were enrolled in a face-to-face Spanish language course, 8 in a hybrid format, and 30 in a fully asynchronous online course.
To breakdown the make-up of the participant pool, 40 first-year, 28 second-year, 13 third-year, and 10 fourth-year students participated in that study.

Framing the analysis around the RQs helps so:

- RQ1: How effective are online classes according to self-reported measures of language abilities?

In order to answer this question, we asked the participants to report if they feel like their language abilities have improved this semester or not.

```{r, improvement, echo=F}
tidy_data %>%
  group_by(progress) %>%
  summarize(., totals = n_distinct(responseid)) %>%  View

# No 5
# Yes 82

```

Of the participants that were included in the analysis, 82 responded "Yes", while 5 responded "No". 
The overwhelming majority (97.7%) reported improvements on language abilities compared to 5.7% who responded "No". 
To further look into where these improvements were made, we can turn to the amount of practice they self-reported receiving in the four areas of language learning that are focused on in classroom: reading, writing, listening, and speaking. 
Participants self-reported on a scale of 1-5, where 1 is no practice and 5 is a lot of practice, how much practice they perceived receiving in class in all of those areas. 
We calculated mean scores for each area and can be seen in the following table:

| **Language skill** | **Mean score** | **Mode** |
| :----------------- | :------------- | :------- |
| Reading            | 3.953          | 4        |
| Writing            | 3.872          | 4        |
| Listening          | 3.581          | 4        |
| Speaking           | 3.744          | 4        |

As can be seen in the above table, it appears that students perceive an average score of 3.744 to 3.953. 
The mode rating for each of these skills is 4. 
Looking at bit deeper at the impact of various factors on these self-reporting ratings, we conducted an Ordinal Regression (**check this**) via the polr package (**cite here**) on R (**cite here**). 
An ordinal regression was run with class format (online, in person, or hybrid) was used as a predictor of practice rating (Likert scale rating of 1-5), type of practice (reading, writing, listening, or speaking), and progress (yes/no if they believed they have made progress as a result of this course). 
Th
**talk about results here w/ numbers**

To answer the question: "How does our new post-pandemic reality modulate tendencies in language enrollment (in person vs online)?" we asked about the participants motivations for taking a language course and which class format is easiest for them to stay motivated in. 
Looking solely at average respondents to the survey question, "Is it easier to stay motivated in an online or face-to-face class format?", the majority of responses (78%) believe it is easier to stay motivated in a face-to-face class than in an online one. 
Table #? shows the breakdown of responses:

| **Class format** | **# of response** |
| :--------------- | :---------------- |
| Face-to-face     | 71                |
| Online           | 14                |
| No response      | 6                 |

To gauge their thoughts on efficiency and effectiveness of online teaching, the participants, who had spent the pandemic taking courses online, were also asked the question, "Do you think online education is similar to face-to-face, or is it more efficient?". 
The breakdown of the responses were as follows:

| **Effectiveness** | **# of response** | **%**  |
| :---------------- | :---------------- | :----- |
| More efficient    | 12                | 13.12% |
| Neither           | 55                | 60.44% |
| Similar           | 19                | 20.88% |
| No response       | 5                 | 5.49%  |

The participants were also asked to rate on a Likert scale how effective they believed online language courses are as compared to face-to-face courses. 
The response breakdown is as follows:

| **Effectiveness score** | **# of responses** |
| :---------------------- | :----------------- |
| 1                       | 6                  |
| 2                       | 16                 |
| 3                       | 36                 |
| 4                       | 24                 |
| 5                       | 3                  |

The mean response is 3.024 and the mode, as shown in the above table, is 3. 
To explore how various factors impacted these responses, **stats here lol**.

### 2022-11-10 scripts/02_tidy_survey_skratch.R

@@ -115,3 +115,82 @@ tidy_data %>%
 # online classes before covid either stick to online or go back to in person
 
 
+
+# I want to look at practice by skill, like average #
+# So i should filter?
+
+reading_data <- tidy_data %>%
+  filter(practice == "reading")
+
+reading_data %>%
+  summary(practicerate) %>%  View
+
+# Results:
+# Min.   :1.000
+# 1st Qu.:3.000
+# Median :4.000
+# Mean   :3.953
+# 3rd Qu.:5.000
+# Max.   :5.000
+
+
+writing_data <- tidy_data %>%
+  filter(practice == "writing")
+
+table(writing_data['practicerate'])
+
+# results
+# Min.   :1.000
+# 1st Qu.:3.000
+# Median :4.000
+# Mean   :3.872
+# 3rd Qu.:5.000
+# Max.   :5.000
+
+
+listening_data <- tidy_data %>%
+  filter(practice == "listening")
+
+table(listening_data['practicerate'])
+
+# results
+# Min.   :1.000
+# 1st Qu.:3.000
+# Median :4.000
+# Mean   :3.581
+# 3rd Qu.:4.000
+# Max.   :5.000
+
+speaking_data <- tidy_data %>%
+  filter(practice == "speaking")
+
+table(speaking_data['practicerate'])
+
+# results
+# Min.   :1.000
+# 1st Qu.:3.000
+# Median :4.000
+# Mean   :3.744
+# 3rd Qu.:4.000
+# Max.   :5.000
+
+
+# we need info on # of responses of face-to-face vs online
+# and i'm too lazy to filter and make this nice so i'm cheating lol
+table(reading_data['motivation.1'])
+
+# face-to-face: 71
+# online: 14
+# blanks: 6
+
+# going to do the same thing to cheat and look at efficiency
+table(reading_data['effective'])
+
+#  1  2  3  4  5
+#  6 16 36 24  3
+
+table(reading_data['efficient'])
+
+#    More efficient        Niether        Similar
+# 5             12             55             19
+

### 2023-01-09 docs/draft/draft.Rmd
Intro+teoria

--- 2022-11-03 docs/draft/draft.Rmd
@@
 
+pero claro el esta lli @lee2022factors lkasla
+
 # Literature Review
 
-- Look at format of the other papers that we have saved in this repo
+The development of online education has been evolving over the past few decades, offering an alternative to deliver learning in a more convenient manner to individuals who could not be physically present in the traditional educational classroom.
+Of special interest is the research and development of language education across time and how online education has played a role in this development, as well as the implementation of communicative strategies within it.
+Research and technological advances allowed online language education to develop greatly, however, the Covid-19 pandemic appeared to be its hardest challenge to date.
+According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses.
+Compared to fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs.
+6.0 million) and a 186 percent increase in undergraduate students enrolled exclusively in online courses (7.0 million vs.
+2.4 million).
+
+Online learning comes with a new set of challenges that are not found in a traditional classroom setting, especially when, for many, it was not an option to have class anywhere but virtually.
+Being forced to switch modalities had consequences, both from the teachers’ and students’ perspectives, as they were either not ready for the change or lacked many materials.
+Top Hat (2020) did a major survey on undergraduate students’ and teachers’ perceptions during the online emergency switch in US universities.
+Their findings within students taking a language class were that overall, the quality of instruction received was worse in comparison to the in-person learning setting.
+In the same way, a vast majority of students felt that the class experience was unengaging as they missed spending time with faculty and fellow students.
+Within this swift change to online settings, many students also found that their academic load was not only reduced but also experienced problems with using online tools.
+
+Language attitudes are key in the language learning environment, as they can determine the success of a student (e.g., Thompson, 2021).
+A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged.
+Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities (Alqurashi, 2016; Horvat et al., 2015; Ke & Kwak, 2013; Wurst et al., 2008).
+Within this framework, anxiety has been linked in several research studies (e.g., Teimouri et al., 2019) as an indicator of poor linguistic development.
+Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment.
+Furthermore, Webb et al.
+(2014) studied the attitudes of students and teachers in a flipped online classroom of Chinese.
+Their results showed an incremental fluctuation in their perception.
+That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term.
+A similar psychological development is observed in Ushida’s (2005) study which investigated the changes in students’ attitudes and motivation over time in online language courses.
+Their results showed a similar evolution within the student’s attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term.
+Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al.
+2018), as well as the familiarity and complexity of the instruments that the course requires (Heckel & Ringeisen, 2019), which might involve some training and assistance before the beginning of the online course.
+During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, Moser et al.
+(2021), leading to an overall feeling of less effective education Top hat (2020), Hodges et al.
+(2020), Lee (2021).
+While the immediate transition to online education seemed rushed in Ana Ruiz-Alonso-Bartol et al (YEAR) the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting.
+Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format.
+Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments Chakraborty et al.
+(2020).
+The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years.
+This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education.
+With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes.
+The goal of this paper is dual, first to determine if online education is still in demand among our undergraduate students, and to identify what are the attitudes towards it in a context where online education is no longer mandatory.
+Our second goal is to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.
+
+# Research gap and theoretical approach
+
+Education mirrors society and its challenges, with Covid-19 as a global example of the adaptations that educators around the world had to implement in order to continue providing education to their students.
+In this sense, education can be understood as a continuum that has endlessly developed according to the socioeconomic changes that society experiences throughout history.
+
+Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years.
+The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education.
+Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment.
+To better understand these tendencies, we employed the lens of The Grounded Theory, as it allows a cyclical observation of a changing world.
+The Grounded Theory considers a changing environment that can evolve, becoming the researcher a constant observer of the changes produced (Hernández Carrera, 2014).
+Having a better understanding of the constant change of tendencies that affect our students can help us not only to provide them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.
+
+This theoretical approach allowed us to perform mixed models including qualitative, quantitative, and open questionary deriving the hypothesis we present in this paper.
+This approach was chosen as it allows the researcher to observe a constant change in tendencies and derive a hypothesis based on the collected data.
+Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them (Corbin & Strauss, 2014).
 

### 2023-01-09 docs/draft/draft.tex
Intro+teoria

--- 2023-01-09 docs/draft/draft.Rmd
@@
----
-title             : "The title"
-shorttitle        : "Title"
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  man]{apa6}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+% Manuscript styling
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
 
-author: 
-  - name          : "First Author"
-    affiliation   : "1"
-    corresponding : yes    # Define only one corresponding author
-    address       : "Postal address"
-    email         : "my@email.com"
-    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
-      - Conceptualization
-      - Writing - Original Draft Preparation
-      - Writing - Review & Editing
-  - name          : "Ernst-August Doelle"
-    affiliation   : "1,2"
-    role:
-      - Writing - Review & Editing
+% Table formatting
+\usepackage{longtable}
+\usepackage{lscape}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
 
-affiliation:
-  - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
-  - id            : "2"
-    institution   : "Konstanz Business School"
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
-authornote: |
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
+\makeatother
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
+\keywords{keywords\newline\indent Word count: X}
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
+\usepackage{lineno}
+
+\linenumbers
+\usepackage{csquotes}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={The title},
+  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
+  pdflang={en-EN},
+  pdfkeywords={keywords},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+
+\title{The title}
+\author{First Author\textsuperscript{1} \& Ernst-August Doelle\textsuperscript{1,2}}
+\date{}
+
+\shorttitle{Title}
+
+\authornote{
+
 Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
@@
 
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+The authors made the following contributions. First Author: Conceptualization, Writing - Original Draft Preparation, Writing - Review \& Editing; Ernst-August Doelle: Writing - Review \& Editing.
 
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
+Correspondence concerning this article should be addressed to First Author, Postal address. E-mail: \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
 
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
+}
 
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
 
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
+\abstract{%
+One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
 
-  One or two sentences to put the results into a more **general context**.
+Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
 
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
+One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
 
-  <!-- https://tinyurl.com/ybremelq -->
+One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
 
-keywords          : "keywords"
-wordcount         : "X"
+Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
 
-bibliography      : ["r-references.bib"]
+One or two sentences to put the results into a more \textbf{general context}.
 
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
+Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+}
 
-documentclass     : "apa6"
-classoption       : "man"
-output            : papaja::apa6_pdf
----
+\begin{document}
+\maketitle
 
-```{r setup, include = FALSE}
-library("papaja")
-r_refs("r-references.bib")
-```
-
-# Introduction
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 
-- Address the general idea
+\begin{itemize}
+\item
+  Address the general idea
+\item
+  Explain the study
+\item
+  Address our contribution
+\end{itemize}
 
-- Explain the study
+pero claro el esta lli (\textbf{lee2022factors?}) lkasla
 
-- Address our contribution
-
-pero claro el esta lli @lee2022factors lkasla
-
-# Literature Review
+\hypertarget{literature-review}{%
+\section{Literature Review}\label{literature-review}}
 
@@
 According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses.
-Compared to fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs.
-6.0 million) and a 186 percent increase in undergraduate students enrolled exclusively in online courses (7.0 million vs.
-2.4 million).
+Compared to fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs.~6.0 million) and a 186 percent increase in undergraduate students enrolled exclusively in online courses (7.0 million vs.~2.4 million).
 
 Online learning comes with a new set of challenges that are not found in a traditional classroom setting, especially when, for many, it was not an option to have class anywhere but virtually.
-Being forced to switch modalities had consequences, both from the teachers’ and students’ perspectives, as they were either not ready for the change or lacked many materials.
-Top Hat (2020) did a major survey on undergraduate students’ and teachers’ perceptions during the online emergency switch in US universities.
+Being forced to switch modalities had consequences, both from the teachers' and students' perspectives, as they were either not ready for the change or lacked many materials.
+Top Hat (2020) did a major survey on undergraduate students' and teachers' perceptions during the online emergency switch in US universities.
 Their findings within students taking a language class were that overall, the quality of instruction received was worse in comparison to the in-person learning setting.
@@
 A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged.
-Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities (Alqurashi, 2016; Horvat et al., 2015; Ke & Kwak, 2013; Wurst et al., 2008).
+Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities (Alqurashi, 2016; Horvat et al., 2015; Ke \& Kwak, 2013; Wurst et al., 2008).
 Within this framework, anxiety has been linked in several research studies (e.g., Teimouri et al., 2019) as an indicator of poor linguistic development.
 Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment.
-Furthermore, Webb et al.
-(2014) studied the attitudes of students and teachers in a flipped online classroom of Chinese.
+Furthermore, Webb et al.~(2014) studied the attitudes of students and teachers in a flipped online classroom of Chinese.
 Their results showed an incremental fluctuation in their perception.
 That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term.
-A similar psychological development is observed in Ushida’s (2005) study which investigated the changes in students’ attitudes and motivation over time in online language courses.
-Their results showed a similar evolution within the student’s attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term.
-Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al.
-2018), as well as the familiarity and complexity of the instruments that the course requires (Heckel & Ringeisen, 2019), which might involve some training and assistance before the beginning of the online course.
-During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, Moser et al.
-(2021), leading to an overall feeling of less effective education Top hat (2020), Hodges et al.
-(2020), Lee (2021).
+A similar psychological development is observed in Ushida's (2005) study which investigated the changes in students' attitudes and motivation over time in online language courses.
+Their results showed a similar evolution within the student's attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term.
+Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al.~2018), as well as the familiarity and complexity of the instruments that the course requires (Heckel \& Ringeisen, 2019), which might involve some training and assistance before the beginning of the online course.
+During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, Moser et al.~(2021), leading to an overall feeling of less effective education Top hat (2020), Hodges et al.~(2020), Lee (2021).
 While the immediate transition to online education seemed rushed in Ana Ruiz-Alonso-Bartol et al (YEAR) the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting.
 Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format.
-Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments Chakraborty et al.
-(2020).
+Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments Chakraborty et al.~(2020).
 The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years.
@@
 
-# Research gap and theoretical approach
+\hypertarget{research-gap-and-theoretical-approach}{%
+\section{Research gap and theoretical approach}\label{research-gap-and-theoretical-approach}}
 
@@
 This approach was chosen as it allows the researcher to observe a constant change in tendencies and derive a hypothesis based on the collected data.
-Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them (Corbin & Strauss, 2014).
+Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them (Corbin \& Strauss, 2014).
 
-# Current Study
+\hypertarget{current-study}{%
+\section{Current Study}\label{current-study}}
 
@@
 
-# Methods
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
-## RQs
+\hypertarget{rqs}{%
+\subsection{RQs}\label{rqs}}
 
@@
 
-- How effective are online classes according to self-reported measures of language abilities?
-
-- How does our new post-pandemic reality modulate tendencies in language enrollment (in person vs online)?
+\begin{itemize}
+\item
+  How effective are online classes according to self-reported measures of language abilities?
+\item
+  How does our new post-pandemic reality modulate tendencies in language enrollment (in person vs online)?
+\end{itemize}
 
@@
 
-## Participants
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
 
@@
 They were all typical university aged students (ages from 18-25) except one student, who belongs to the 25-35 age range.
-[I don't know if this will be relevant, probably not, but we could include: 35 of the students were first years, 27 were second years, 11 were third years, and 9 were fourth years.] 
-Of the # participants who completed the survey, 23 were taking a fully asynchronous online Spanish class, 51 were taking an in person class, and 7 were taking a hybrid course.
+{[}I don't know if this will be relevant, probably not, but we could include: 35 of the students were first years, 27 were second years, 11 were third years, and 9 were fourth years.{]}
+Of the \# participants who completed the survey, 23 were taking a fully asynchronous online Spanish class, 51 were taking an in person class, and 7 were taking a hybrid course.
 
 We also collected information about their linguistic backgrounds.
-Of the # of participants, 37 of the students speak another language besides English and Spanish. 
+Of the \# of participants, 37 of the students speak another language besides English and Spanish.
 The participants reported learning Spanish between the ages of X and X.
@@
 
-## Material and Procedure
+\hypertarget{material-and-procedure}{%
+\subsection{Material and Procedure}\label{material-and-procedure}}
 
 The survey was created on Qualtrics.
-It was distributed via an online anonymous link to undergraduate students taking Spanish courses in a large university located in the northeast United States and it took an average of # minutes to complete (find this info on qualtrics).
+It was distributed via an online anonymous link to undergraduate students taking Spanish courses in a large university located in the northeast United States and it took an average of \# minutes to complete (find this info on qualtrics).
 In total, the participants answered 46 questions.
@@
 
-The aforementioned sections of the survey followed a mixed-methods design to examine students’ perspectives through an interaction of quantitative and qualitative questions.
-By using open-ended and close-ended questionnaires we were able to collect, contrast and students’ testimonies. 
+The aforementioned sections of the survey followed a mixed-methods design to examine students' perspectives through an interaction of quantitative and qualitative questions.
+By using open-ended and close-ended questionnaires we were able to collect, contrast and students' testimonies.
 The mixed-methods design of this study allowed us to compare open-ended questions, with close-ended questions obtaining tendencies, preferences, as well as attitudes toward enrollment.
-Close-ended quantitative questions were presented in a scale from 5 to 1 in the questionnaire, with a 5 being valued as “very useful” and a 1 as “not very useful”.
+Close-ended quantitative questions were presented in a scale from 5 to 1 in the questionnaire, with a 5 being valued as ``very useful'' and a 1 as ``not very useful''.
 
-## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
+\hypertarget{data-analysis}{%
+\subsection{Data analysis}\label{data-analysis}}
 
-# Results
+We used R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{papaja} (Version 0.1.1; Aust \& Barth, 2022), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) for all our analyses.
 
-# Discussion
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
-- Tie to RQs and big picture
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 
-# Conclusion
+\begin{itemize}
+\tightlist
+\item
+  Tie to RQs and big picture
+\end{itemize}
 
-- Big Picture
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 
-- Limitations
-
-- Future directions
+\begin{itemize}
+\item
+  Big Picture
+\item
+  Limitations
+\item
+  Future directions
+\end{itemize}
 
@@
 
-# References
+\hypertarget{references}{%
+\section{References}\label{references}}
 
-::: {#refs custom-style="Bibliography"}
-:::
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
+Aust, F., \& Barth, M. (2022). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
+Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://cran.r-project.org/package=tinylabels}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
+R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\end{CSLReferences}
+
+\end{document}

### 2023-01-09 docs/draft/draft.Rmd
intro+teoria
Bibiografia arreglada

@@
 
-pero claro el esta lli @lee2022factors lkasla
+\newpage
 
@@
 
-Language attitudes are key in the language learning environment, as they can determine the success of a student (e.g., Thompson, 2021).
+Language attitudes are key in the language learning environment, as they can determine the success of a student [ eg @thompson2021attitudes].
 A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged.
-Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities (Alqurashi, 2016; Horvat et al., 2015; Ke & Kwak, 2013; Wurst et al., 2008).
-Within this framework, anxiety has been linked in several research studies (e.g., Teimouri et al., 2019) as an indicator of poor linguistic development.
+Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities [ @alqurashi2016self; @horvat2015student; @ke2013constructs; @lan2010using].
+Within this framework, anxiety has been linked in several research studies [e.g.,@teimouri2019second] as an indicator of poor linguistic development.
 Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment.
-Furthermore, Webb et al.
-(2014) studied the attitudes of students and teachers in a flipped online classroom of Chinese.
+Furthermore, @webb2014flipping studied the attitudes of students and teachers in a flipped online classroom of Chinese.
 Their results showed an incremental fluctuation in their perception.
 That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term.
-A similar psychological development is observed in Ushida’s (2005) study which investigated the changes in students’ attitudes and motivation over time in online language courses.
+A similar psychological development is observed in @ushida2005role study which investigated the changes in students’ attitudes and motivation over time in online language courses.
 Their results showed a similar evolution within the student’s attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term.
 Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al.
-2018), as well as the familiarity and complexity of the instruments that the course requires (Heckel & Ringeisen, 2019), which might involve some training and assistance before the beginning of the online course.
-During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, Moser et al.
-(2021), leading to an overall feeling of less effective education Top hat (2020), Hodges et al.
-(2020), Lee (2021).
-While the immediate transition to online education seemed rushed in Ana Ruiz-Alonso-Bartol et al (YEAR) the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting.
+2018), as well as the familiarity and complexity of the instruments that the course requires (@heckel2019pride), which might involve some training and assistance before the beginning of the online course.
+During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, @tomasik2021educational, leading to an overall feeling of less effective education Top hat (2020), @hodges2020difference, @lee2022factors.
+While the immediate transition to online education seemed rushed in @ruiz2022transitioning the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting.
 Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format.
-Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments Chakraborty et al.
-(2020).
+Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments [@chakraborty2021opinion].
 The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years.
@@
 To better understand these tendencies, we employed the lens of The Grounded Theory, as it allows a cyclical observation of a changing world.
-The Grounded Theory considers a changing environment that can evolve, becoming the researcher a constant observer of the changes produced (Hernández Carrera, 2014).
+The Grounded Theory considers a changing environment that can evolve, becoming the researcher a constant observer of the changes produced [@hernandez2014investigacion].
 Having a better understanding of the constant change of tendencies that affect our students can help us not only to provide them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.
@@
 This approach was chosen as it allows the researcher to observe a constant change in tendencies and derive a hypothesis based on the collected data.
-Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them (Corbin & Strauss, 2014).
+Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them [@corbin2014basics].
 

### 2023-01-09 docs/draft/draft.tex
intro+teoria
Bibiografia arreglada

@@
 
-pero claro el esta lli (\textbf{lee2022factors?}) lkasla
+\newpage
 
@@
 
-Language attitudes are key in the language learning environment, as they can determine the success of a student (e.g., Thompson, 2021).
+Language attitudes are key in the language learning environment, as they can determine the success of a student (eg Thompson, 2021).
 A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged.
-Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities (Alqurashi, 2016; Horvat et al., 2015; Ke \& Kwak, 2013; Wurst et al., 2008).
-Within this framework, anxiety has been linked in several research studies (e.g., Teimouri et al., 2019) as an indicator of poor linguistic development.
+Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities (Alqurashi et al., 2016; Horvat, Dobrota, Krsmanovic, \& Cudanov, 2015; Ke \& Kwak, 2013; Lan \& Sie, 2010).
+Within this framework, anxiety has been linked in several research studies (e.g., Teimouri, Goetze, \& Plonsky, 2019) as an indicator of poor linguistic development.
 Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment.
-Furthermore, Webb et al.~(2014) studied the attitudes of students and teachers in a flipped online classroom of Chinese.
+Furthermore, Webb, Doman, and Pusey (2014) studied the attitudes of students and teachers in a flipped online classroom of Chinese.
 Their results showed an incremental fluctuation in their perception.
 That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term.
-A similar psychological development is observed in Ushida's (2005) study which investigated the changes in students' attitudes and motivation over time in online language courses.
+A similar psychological development is observed in Ushida (2005) study which investigated the changes in students' attitudes and motivation over time in online language courses.
 Their results showed a similar evolution within the student's attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term.
-Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al.~2018), as well as the familiarity and complexity of the instruments that the course requires (Heckel \& Ringeisen, 2019), which might involve some training and assistance before the beginning of the online course.
-During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, Moser et al.~(2021), leading to an overall feeling of less effective education Top hat (2020), Hodges et al.~(2020), Lee (2021).
-While the immediate transition to online education seemed rushed in Ana Ruiz-Alonso-Bartol et al (YEAR) the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting.
+Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al.~2018), as well as the familiarity and complexity of the instruments that the course requires (Heckel and Ringeisen (2019)), which might involve some training and assistance before the beginning of the online course.
+During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, Tomasik, Helbling, and Moser (2021), leading to an overall feeling of less effective education Top hat (2020), Hodges, Moore, Lockee, Trust, and Bond (2020), Lee (2022).
+While the immediate transition to online education seemed rushed in Ruiz-Alonso-Bartol, Querrien, Dykstra, Fernández-Mira, and Sánchez-Gutiérrez (2022) the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting.
 Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format.
-Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments Chakraborty et al.~(2020).
+Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments (Chakraborty, Mittal, Gupta, Yadav, \& Arora, 2021).
 The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years.
@@
 To better understand these tendencies, we employed the lens of The Grounded Theory, as it allows a cyclical observation of a changing world.
-The Grounded Theory considers a changing environment that can evolve, becoming the researcher a constant observer of the changes produced (Hernández Carrera, 2014).
+The Grounded Theory considers a changing environment that can evolve, becoming the researcher a constant observer of the changes produced (Hernandez Carrera, 2014).
 Having a better understanding of the constant change of tendencies that affect our students can help us not only to provide them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-alqurashi2016self}{}}%
+Alqurashi, E. et al. (2016). Self-efficacy in online learning environments: A literature review. \emph{Contemporary Issues in Education Research (CIER)}, \emph{9}(1), 45--52.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-chakraborty2021opinion}{}}%
+Chakraborty, P., Mittal, P., Gupta, M.
+S., Yadav, S., \& Arora, A.
+(2021).
+Opinion of students on online education during the COVID-19 pandemic.
+\emph{Human Behavior and Emerging Technologies}, \emph{3}(3), 357--365.
+
+\leavevmode\vadjust pre{\hypertarget{ref-corbin2014basics}{}}%
+Corbin, J., \& Strauss, A. (2014). \emph{Basics of qualitative research: Techniques and procedures for developing grounded theory}. Sage publications.
+
+\leavevmode\vadjust pre{\hypertarget{ref-heckel2019pride}{}}%
+Heckel, C., \& Ringeisen, T.
+(2019).
+Pride and anxiety in online learning environments: Achievement emotions as mediators between learners' characteristics and learning outcomes.
+\emph{Journal of Computer Assisted Learning}, \emph{35}(5), 667--677.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hernandez2014investigacion}{}}%
+Hernandez Carrera, R. M. (2014). La investigacion cualitativa a trav{e}s de entrevistas: Su analisis mediante la teoria fundamentada. \emph{Cuestiones Pedagogicas, 23, 187-210}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-hodges2020difference}{}}%
+Hodges, C. B., Moore, S., Lockee, B. B., Trust, T., \& Bond, M. A. (2020). \emph{The difference between emergency remote teaching and online learning}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-horvat2015student}{}}%
+Horvat, A., Dobrota, M., Krsmanovic, M., \& Cudanov, M.
+(2015).
+Student perception of moodle learning management system: A satisfaction and significance analysis.
+\emph{Interactive Learning Environments}, \emph{23}(4), 515--527.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ke2013constructs}{}}%
+Ke, F., \& Kwak, D.
+(2013).
+Constructs of student-centered online learning on learning satisfaction of a diverse online student body: A structural equation modeling approach.
+\emph{Journal of Educational Computing Research}, \emph{48}(1), 97--122.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lan2010using}{}}%
+Lan, Y.-F., \& Sie, Y.-S. (2010). Using RSS to support mobile learning based on media richness theory. \emph{Computers \& Education}, \emph{55}(2), 723--732.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lee2022factors}{}}%
+Lee, S.-M. (2022). Factors affecting the quality of online learning in a task-based college course. \emph{Foreign Language Annals}, \emph{55}(1), 116--134.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
 R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ruiz2022transitioning}{}}%
+Ruiz-Alonso-Bartol, A., Querrien, D., Dykstra, S., Fernández-Mira, P., \& Sánchez-Gutiérrez, C.
+(2022).
+Transitioning to emergency online teaching: The experience of spanish language learners in a US university.
+\emph{System}, \emph{104}, 102684.
+
+\leavevmode\vadjust pre{\hypertarget{ref-teimouri2019second}{}}%
+Teimouri, Y., Goetze, J., \& Plonsky, L. (2019). Second language anxiety and achievement: A meta-analysis. \emph{Studies in Second Language Acquisition}, \emph{41}(2), 363--387.
+
+\leavevmode\vadjust pre{\hypertarget{ref-thompson2021attitudes}{}}%
+Thompson, A. S. (2021). Attitudes and beliefs. In \emph{The routledge handbook of the psychology of language learning and teaching} (pp. 149--160). Routledge.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tomasik2021educational}{}}%
+Tomasik, M.
+J., Helbling, L.
+A., \& Moser, U.
+(2021).
+Educational gains of in-person vs.
+Distance learning in primary and secondary schools: A natural experiment during the COVID-19 pandemic school closures in switzerland.
+\emph{International Journal of Psychology}, \emph{56}(4), 566--576.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ushida2005role}{}}%
+Ushida, E. (2005). The role of students' attitudes and motivation in second language learning in online language courses. \emph{CALICO Journal}, 49--78.
+
+\leavevmode\vadjust pre{\hypertarget{ref-webb2014flipping}{}}%
+Webb, M., Doman, E., \& Pusey, K. (2014). Flipping a chinese university EFL course: What students and teachers think of the model. \emph{The Journal of Asia TEFL}, \emph{11}(4), 53--87.
 

### 2023-01-17 docs/draft/draft.Rmd
formatting changes
stopped at line 103

@@
 
-The development of online education has been evolving over the past few decades, offering an alternative to deliver learning in a more convenient manner to individuals who could not be physically present in the traditional educational classroom.
+The development of online education has been evolving over the past few decades, offering an alternative to delivering learning in a more convenient manner to individuals who could not be physically present in the traditional educational classroom.
+<!--- we might consider (not rn but to be discussed) deleted the "could not be physically present" part, it could open a can of worms---> 
 Of special interest is the research and development of language education across time and how online education has played a role in this development, as well as the implementation of communicative strategies within it.
-Research and technological advances allowed online language education to develop greatly, however, the Covid-19 pandemic appeared to be its hardest challenge to date.
-According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses.
-Compared to fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs.
+<!--- I think the above sentence might be unnecessary bc we don't necessarily talk about communicative strategies --> 
+Research and technological advances allowed online language education to develop greatly, <!--- for example, x, y, z helps students to do a, b, and c. then start with the next sentence--->  
+However, the Covid-19 pandemic appeared to be its hardest challenge to date.
+<!--- in what way?
+are we saying covid was a challenge for online learning?
+this seems to go against the previous sentences saying that techology had advanced and online learning has developed-->
+According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses (*insert citation*).
+Compared to Fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs.
 6.0 million) and a 186 percent increase in undergraduate students enrolled exclusively in online courses (7.0 million vs.
@@
 Top Hat (2020) did a major survey on undergraduate students’ and teachers’ perceptions during the online emergency switch in US universities. 
-Their findings within students taking a language class were that overall, the quality of instruction received was worse in comparison to the in-person learning setting.
+Their findings within students taking a language class were that overall, the quality of instruction received was worse in comparison to the in-person learning setting (*insert citation*)
 In the same way, a vast majority of students felt that the class experience was unengaging as they missed spending time with faculty and fellow students. 
 Within this swift change to online settings, many students also found that their academic load was not only reduced but also experienced problems with using online tools.
+<!--- i'm going to think about how to reframe this paragraph --->
 
@@
 Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments [@chakraborty2021opinion].
+
 The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years. 

### 2023-01-17 docs/draft/draft.Rmd
draft comments

@@
 
-** big picture = social implications of online teaching and how that has changed in a post-pandemic world
-** small picture = what we are doing in this language program and how can we improve to meet the needs and wants of the students in their new reality
-
-- Address the general idea
-
-- Explain the study
-
-- Address our contribution
-
-\newpage
-
-# Literature Review
-
 The development of online education has been evolving over the past few decades, offering an alternative to delivering learning in a more convenient manner to individuals who could not be physically present in the traditional educational classroom.
@@
 
-Online learning comes with a new set of challenges that are not found in a traditional classroom setting, especially when, for many, it was not an option to have class anywhere but virtually. 
-Being forced to switch modalities had consequences, both from the teachers’ and students’ perspectives, as they were either not ready for the change or lacked many materials. 
-Top Hat (2020) did a major survey on undergraduate students’ and teachers’ perceptions during the online emergency switch in US universities. 
-Their findings within students taking a language class were that overall, the quality of instruction received was worse in comparison to the in-person learning setting (*insert citation*)
-In the same way, a vast majority of students felt that the class experience was unengaging as they missed spending time with faculty and fellow students. 
-Within this swift change to online settings, many students also found that their academic load was not only reduced but also experienced problems with using online tools.
-<!--- i'm going to think about how to reframe this paragraph --->
-
-Language attitudes are key in the language learning environment, as they can determine the success of a student [ eg @thompson2021attitudes]. 
-A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged.
-Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities [ @alqurashi2016self; @horvat2015student; @ke2013constructs; @lan2010using].
-Within this framework, anxiety has been linked in several research studies [e.g.,@teimouri2019second] as an indicator of poor linguistic development. 
-Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment. 
-Furthermore, @webb2014flipping studied the attitudes of students and teachers in a flipped online classroom of Chinese. 
+Language attitudes are key in the language learning environment, as they can determine the success of a student [eg @thompson2021attitudes].
+<!--- lets avoid statements that are very direct and assertive like that, something more like "they play a role in determining the success of a student --->
+A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged (*insert citation*).
+Interestingly, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities [@alqurashi2016self; @horvat2015student; @ke2013constructs; @lan2010using].
+Within this framework <!---i'm not sure that framework is the right word here-->, anxiety has been linked in several research studies [e.g.,@teimouri2019second] as an indicator of poor linguistic development.
+<!--- i think this sentence should be deleted "Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment." --> 
+<!--- i'm going to think about how to rework these examples into a paragraph that flows a little better Furthermore, @webb2014flipping studied the attitudes of students and teachers in a flipped online classroom of Chinese.
 Their results showed an incremental fluctuation in their perception. 
@@
 Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments [@chakraborty2021opinion].
+--->
 
 The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years. 
-This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education. 
+<!--- This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education.
+- maybe delete this --->
 With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes.
-The goal of this paper is dual, first to determine if online education is still in demand among our undergraduate students, and to identify what are the attitudes towards it in a context where online education is no longer mandatory.
-Our second goal is to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.
+<!--- idk if we can say "global decrease" maybe something like "with a push to return to pre-covid practices" --->
+The goal of this paper is twofold, first to identify attitudes towards online language education it in a context where online education is no longer mandatory and to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.
 
-# Research gap and theoretical approach
+\newpage
 
-Education mirrors society and its challenges, with Covid-19 as a global example of the adaptations that educators around the world had to implement in order to continue providing education to their students.
-In this sense, education can be understood as a continuum that has endlessly developed according to the socioeconomic changes that society experiences throughout history.
+# Previous literature and theoretical framework
 
-Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. 
+<!--- i don't know if this paragraph is necessary "Education mirrors society and its challenges, with Covid-19 as a global example of the adaptations that educators around the world had to implement in order to continue providing education to their students.
+In this sense, education can be understood as a continuum that has endlessly developed according to the socioeconomic changes that society experiences throughout history." --->
+
+The goal of the current paper is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. 
 The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education. 
 Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment.
-To better understand these tendencies, we employed the lens of The Grounded Theory, as it allows a cyclical observation of a changing world. 
-The Grounded Theory considers a changing environment that can evolve, becoming the researcher a constant observer of the changes produced [@hernandez2014investigacion]. 
-Having a better understanding of the constant change of tendencies that affect our students can help us not only to provide them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.
 
-This theoretical approach allowed us to perform mixed models including qualitative, quantitative, and open questionary deriving the hypothesis we present in this paper. 
-This approach was chosen as it allows the researcher to observe a constant change in tendencies and derive a hypothesis based on the collected data.  
+<!-- i think this is what needs to be worked on, if you have something in the introcution that fits in any of these categories, add it below and we can work it into a few paragraph to motivate the study --->
+
+## Online learning
+
+#### Effectiveness
+
+#### Motivation
+
+#### Perception / attitudes
+
+## Grounded theory
+
+In order to study and understand tendencies in online learning, we turned to Grounded Theory, as it allows for a cyclical observation of a changing world, where the researcher is a constant observer of the changes produced [@hernandez2014investigacion].
+This theoretical approach allowed us to employ a mixed models questionnaire that included qualitative, quantitative, and open-ended questions aimed at gaining information about the participant's experience, attitudes, and motivations for taking online vs.
+in-person language classes.
 Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them [@corbin2014basics].
+<!--- can you elaborate on this?
+--->
 
@@
 
+<!--- i think this is "too personal" we should change it to something like, "the current study aims to explore attitudes towards online instruction at an R1 instution in a post-pandemic reality where learning has been adapted to an online learning environment" o algo asi ...
 Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. 
@@
 Having a better understanding of the constant change of tendencies that affect our students can help us not only in providing them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.
+--->
 

### 2023-01-21 docs/draft/draft.Rmd
Cambios

@@
 
-The development of online education has been evolving over the past few decades, offering an alternative to delivering learning in a more convenient manner to individuals who could not be physically present in the traditional educational classroom.
+The development of online education has been evolving over the past few decades, offering an alternative to delivering learning in a more convenient manner to individuals.
 <!--- we might consider (not rn but to be discussed) deleted the "could not be physically present" part, it could open a can of worms---> 
-Of special interest is the research and development of language education across time and how online education has played a role in this development, as well as the implementation of communicative strategies within it.
-<!--- I think the above sentence might be unnecessary bc we don't necessarily talk about communicative strategies --> 
-Research and technological advances allowed online language education to develop greatly, <!--- for example, x, y, z helps students to do a, b, and c. then start with the next sentence--->  
-However, the Covid-19 pandemic appeared to be its hardest challenge to date.
-<!--- in what way?
-are we saying covid was a challenge for online learning?
-this seems to go against the previous sentences saying that techology had advanced and online learning has developed-->
-According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses (*insert citation*).
+Of particular interest is the research and development of online language education along with technological advances that made possible an evolution in the quality and accessibility of the materials.
+For example, implementing online tools such as Zoom, VoiceThread, FlipGrid, etc, allowed students to hold conversations, share ideas and provide their opinions in a similar way to a traditional online setting.
+
+According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses [@nationalstatistics_2022].
 Compared to Fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs.
@@
 
-Language attitudes are key in the language learning environment, as they can determine the success of a student [eg @thompson2021attitudes].
-<!--- lets avoid statements that are very direct and assertive like that, something more like "they play a role in determining the success of a student --->
-A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged (*insert citation*).
-Interestingly, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities [@alqurashi2016self; @horvat2015student; @ke2013constructs; @lan2010using].
-Within this framework <!---i'm not sure that framework is the right word here-->, anxiety has been linked in several research studies [e.g.,@teimouri2019second] as an indicator of poor linguistic development.
-<!--- i think this sentence should be deleted "Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment." --> 
-<!--- i'm going to think about how to rework these examples into a paragraph that flows a little better Furthermore, @webb2014flipping studied the attitudes of students and teachers in a flipped online classroom of Chinese.
+<!--- I think the above sentence might be unnecessary bc we don't necessarily talk about communicative strategies --> 
+<!--- IAR Two lines convined --> 
+<!--- for example, x, y, z helps students to do a, b, and c. then start with the next sentence--->  
+However, the Covid-19 pandemic appeared to be its hardest challenge to date, as many educators where not prepare for the online transition @tomasik2021educational.
+<!--- in what way?
+are we saying covid was a challenge for online learning?
+this seems to go against the previous sentences saying that techology had advanced and online learning has developed-->
+
+The outbreak of COVID-19 has caused online teaching and learning to evolve rapidly during the past two years due to the national online swift. 
+However, with the progressive decrease in global covid cases, universities are adopting a pre-pandemic approach, making students return to the educational classroom.
+
+<!--- This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education.
+- maybe delete this --->
+With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes.
+<!--- idk if we can say "global decrease" maybe something like "with a push to return to pre-covid practices" --->
+The goal of this paper is twofold, first to identify attitudes towards online language education it in a context where online education is no longer mandatory and, second to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.
+
+\newpage
+
+# Previous literature and theoretical framework
+
+<!--- i don't know if this paragraph is necessary "Education mirrors society and its challenges, with Covid-19 as a global example of the adaptations that educators around the world had to implement in order to continue providing education to their students.
+In this sense, education can be understood as a continuum that has endlessly developed according to the socioeconomic changes that society experiences throughout history."  -esto quizas entraria mejor como primera linea en "the current study"- --->
+
+The goal of the current paper is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. 
+The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education. 
+Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment.
+
+<!-- i think this is what needs to be worked on, if you have something in the introcution that fits in any of these categories, add it below and we can work it into a few paragraph to motivate the study --->
+
+## Online learning
+
+In several decades of existence and development, online learning has never gained more attention than it did over the national pandemic, as 75 percent of undergraduate students were enrolled in at least one online course [@nationalstatistics_2022].
+Previous pre-pandemic research has proven that distance students can archive similar learning goals as those students that were physically present on the educational environment [eg: @mccutcheon2015systematic, @means2013effectiveness, @sun2016online].
+While online learning comes with a set of challenges that are not found in a traditional classroom, such as the ability to self-regulate, and the lack of interaction, it can improve the effectiveness and efficiency of education as it eliminates geographical barriers, improving accessibility, and the ability to learn at the student's pace [@kebritchi2017issues].
+
+During the pandemic, one of the most cited difficulties with the quick transition to online education was the lack of preparation and families with educational tools.
+Being forced to switch moralities had consequences, both from the teachers’ and students’ perspectives, as they were either not ready for the change or lacked many materials.
+[@mahyoob2020challenges] describes how both students and educators found technical problems concerning the use of technology, affecting the adequate distribution of teaching materials and communications among the students.
+These difficulties faded as the teaching force became more familiar with the learning tools. 
+In addition, the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials and therefore gained more experience with their newfound educational setting.
+[@ruiz2022transitioning]
+Likewise, the attitudes toward the online setting evolved throughout the pandemic.
+Increased autonomy and self-paced learning opportunities offered by the new online format were overall the most liked attributes of the change.
+
+#### Effectiveness and attitudes toward online education 
+#Intro online learning history
+
+Language attitudes are essential in the language learning environment, as they play an important role in determining the student's final success in the language course.
+Similarly, a learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged.[eg @thompson2021attitudes] <!--- lets avoid statements that are very direct and assertive like that, something more like "they play a role in determining the success of a student --->
+Not surprisingly, the attitudes in online learning have been shown to play a fundamental role as students are physically detached from the learning environment, and rely more on self-regulation abilities [@alqurashi2016self; @horvat2015student; @ke2013constructs; @lan2010using].
+Within this line of research <!---i'm not sure that framework is the right word here-->, anxiety has been linked in several research studies [e.g.,@teimouri2019second] as an indicator of poor linguistic development.
+<!--- i think this sentence should be deleted "Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment." -como quieras, lo que queria era expresar la idea que a traves de la experiencia y ver el sistema, los niveles de ansiedad disminuyen - -->
+
+@tophatfall2020 did a major survey on undergraduate students’ and teachers’ perceptions at the beginning of the online emergency switch in US universities. 
+Their findings within students taking a language class were that overall, the quality of instruction received was worse in comparison to the in-person learning setting. 
+In the same way, a vast majority of students felt that the class experience was unengaging as they missed spending time with faculty and fellow students. 
+Within this swift change to online settings, many students also found that their academic load was not only reduced but also experienced problems with using online tools.<!--- conexion con como progresivamente la situacion fue mejorando.
+
+<!--- i'm going to think about how to rework these examples into a paragraph that flows a little better
+
+Furthermore, @webb2014flipping studied the attitudes of students and teachers in a flipped online classroom of Chinese. 
 Their results showed an incremental fluctuation in their perception. 
@@
 
-The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years. 
-<!--- This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education.
-- maybe delete this --->
-With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes.
-<!--- idk if we can say "global decrease" maybe something like "with a push to return to pre-covid practices" --->
-The goal of this paper is twofold, first to identify attitudes towards online language education it in a context where online education is no longer mandatory and to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.
-
-\newpage
-
-# Previous literature and theoretical framework
-
-<!--- i don't know if this paragraph is necessary "Education mirrors society and its challenges, with Covid-19 as a global example of the adaptations that educators around the world had to implement in order to continue providing education to their students.
-In this sense, education can be understood as a continuum that has endlessly developed according to the socioeconomic changes that society experiences throughout history." --->
-
-The goal of the current paper is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. 
-The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education. 
-Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment.
-
-<!-- i think this is what needs to be worked on, if you have something in the introcution that fits in any of these categories, add it below and we can work it into a few paragraph to motivate the study --->
-
-## Online learning
-
-#### Effectiveness
-
 #### Motivation
 
-#### Perception / attitudes
+With the decrease in covid cases, most major US universities are looking to transition into face-to-face settings, creating a new reality within language education. 
+A global survey [@widenhorn2023comparing] of more than 5.000 university students revealed that more than four in five students (82%) would still want to have at least some of their courses online after having passed two years of the global pandemic.
+Similarly, two in five university students (41%) would still prefer to continue online without physical interaction with the educational classroom. 
+When asked what factors other than the pandemic had an impact, students replied with the economy (73%), location or transportation (44%), and lack of access to technology (35%)
+This is the most extensive study that tackles the shift toward face-to-face education after the online pandemic to date. 
+However, this study is broad as it covers several countries with different economic needs and transportation necessities. 
+Therefore, our study aims to provide more fine-grained detail about the post-pandemic tendencies in a North Eastern US university ....
 
@@
 In order to study and understand tendencies in online learning, we turned to Grounded Theory, as it allows for a cyclical observation of a changing world, where the researcher is a constant observer of the changes produced [@hernandez2014investigacion].
-This theoretical approach allowed us to employ a mixed models questionnaire that included qualitative, quantitative, and open-ended questions aimed at gaining information about the participant's experience, attitudes, and motivations for taking online vs.
+This theoretical approach allows the research team to explain the relationships among categories within the same reality. 
+It is a constant comparison methodology of data of the reality being studied, where the hypothesis are formulated throughout the research process. 
+This was performed via student evaluations, which allowed to test the thematic coding structuration and check for unanticipated topics. 
+In this step, the most noteworthy categories were selected (axial coding) with the intention of making a posterior analysis (selected coding). 
+A Qualtrics Survey followed this initial observation, which allowed us to employ a mixed models questionnaire that included qualitative, quantitative, and open-ended questions aimed at gaining information about the participant's experience, attitudes, and motivations for taking online vs.
 in-person language classes.
-Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them [@corbin2014basics].
-<!--- can you elaborate on this?
---->
+We then tested each category in... (add statisct analysis used).
+
+Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within a specific area, along with the factors that affect them [@corbin2014basics].
+Thus we understand that the results we obtain might be limited to the area from where the information is being extracted.  
+Social factors such as distance from campus, commuting time, working hours, or access to the internet might be geographically dependent and not extrapolable to other areas or countries.
 

### 2023-01-21 docs/draft/draft.tex
Cambios

@@
 
-** big picture = social implications of online teaching and how that has changed in a post-pandemic world
-** small picture = what we are doing in this language program and how can we improve to meet the needs and wants of the students in their new reality
+The development of online education has been evolving over the past few decades, offering an alternative to delivering learning in a more convenient manner to individuals.
+Of particular interest is the research and development of online language education along with technological advances that made possible an evolution in the quality and accessibility of the materials.
+For example, implementing online tools such as Zoom, VoiceThread, FlipGrid, etc, allowed students to hold conversations, share ideas and provide their opinions in a similar way to a traditional online setting.
 
-\begin{itemize}
-\item
-  Address the general idea
-\item
-  Explain the study
-\item
-  Address our contribution
-\end{itemize}
+According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses (Education Statistics, 2022).
+Compared to Fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs.~6.0 million) and a 186 percent increase in undergraduate students enrolled exclusively in online courses (7.0 million vs.~2.4 million).
+
+However, the Covid-19 pandemic appeared to be its hardest challenge to date, as many educators where not prepare for the online transition Tomasik, Helbling, and Moser (2021).
+
+The outbreak of COVID-19 has caused online teaching and learning to evolve rapidly during the past two years due to the national online swift.
+However, with the progressive decrease in global covid cases, universities are adopting a pre-pandemic approach, making students return to the educational classroom.
+
+With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes.
+The goal of this paper is twofold, first to identify attitudes towards online language education it in a context where online education is no longer mandatory and, second to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.
 
@@
 
-\hypertarget{literature-review}{%
-\section{Literature Review}\label{literature-review}}
+\hypertarget{previous-literature-and-theoretical-framework}{%
+\section{Previous literature and theoretical framework}\label{previous-literature-and-theoretical-framework}}
 
-The development of online education has been evolving over the past few decades, offering an alternative to deliver learning in a more convenient manner to individuals who could not be physically present in the traditional educational classroom.
-Of special interest is the research and development of language education across time and how online education has played a role in this development, as well as the implementation of communicative strategies within it.
-Research and technological advances allowed online language education to develop greatly, however, the Covid-19 pandemic appeared to be its hardest challenge to date.
-According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses.
-Compared to fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs.~6.0 million) and a 186 percent increase in undergraduate students enrolled exclusively in online courses (7.0 million vs.~2.4 million).
+The goal of the current paper is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years.
+The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education.
+Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment.
 
-Online learning comes with a new set of challenges that are not found in a traditional classroom setting, especially when, for many, it was not an option to have class anywhere but virtually.
-Being forced to switch modalities had consequences, both from the teachers' and students' perspectives, as they were either not ready for the change or lacked many materials.
-Top Hat (2020) did a major survey on undergraduate students' and teachers' perceptions during the online emergency switch in US universities.
+\hypertarget{online-learning}{%
+\subsection{Online learning}\label{online-learning}}
+
+In several decades of existence and development, online learning has never gained more attention than it did over the national pandemic, as 75 percent of undergraduate students were enrolled in at least one online course (Education Statistics, 2022).
+Previous pre-pandemic research has proven that distance students can archive similar learning goals as those students that were physically present on the educational environment Sun \& Chen (2016).
+While online learning comes with a set of challenges that are not found in a traditional classroom, such as the ability to self-regulate, and the lack of interaction, it can improve the effectiveness and efficiency of education as it eliminates geographical barriers, improving accessibility, and the ability to learn at the student's pace (Kebritchi, Lipschuetz, \& Santiague, 2017).
+
+During the pandemic, one of the most cited difficulties with the quick transition to online education was the lack of preparation and families with educational tools.
+Being forced to switch moralities had consequences, both from the teachers' and students' perspectives, as they were either not ready for the change or lacked many materials.
+(Mahyoob, 2020) describes how both students and educators found technical problems concerning the use of technology, affecting the adequate distribution of teaching materials and communications among the students.
+These difficulties faded as the teaching force became more familiar with the learning tools.
+In addition, the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials and therefore gained more experience with their newfound educational setting.
+(Ruiz-Alonso-Bartol, Querrien, Dykstra, Fernández-Mira, \& Sánchez-Gutiérrez, 2022)
+Likewise, the attitudes toward the online setting evolved throughout the pandemic.
+Increased autonomy and self-paced learning opportunities offered by the new online format were overall the most liked attributes of the change.
+
+\hypertarget{effectiveness-and-attitudes-toward-online-education}{%
+\paragraph{Effectiveness and attitudes toward online education}\label{effectiveness-and-attitudes-toward-online-education}}
+
+\#Intro online learning history
+
+Language attitudes are essential in the language learning environment, as they play an important role in determining the student's final success in the language course.
+Similarly, a learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged.(eg Thompson, 2021)
+Not surprisingly, the attitudes in online learning have been shown to play a fundamental role as students are physically detached from the learning environment, and rely more on self-regulation abilities (Alqurashi et al., 2016; Horvat, Dobrota, Krsmanovic, \& Cudanov, 2015; Ke \& Kwak, 2013; Lan \& Sie, 2010).
+Within this line of research , anxiety has been linked in several research studies (e.g., Teimouri, Goetze, \& Plonsky, 2019) as an indicator of poor linguistic development.
+
+Hat (2021) did a major survey on undergraduate students' and teachers' perceptions at the beginning of the online emergency switch in US universities.
 Their findings within students taking a language class were that overall, the quality of instruction received was worse in comparison to the in-person learning setting.
@@
 
-Language attitudes are key in the language learning environment, as they can determine the success of a student (eg Thompson, 2021).
-A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged.
-Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities (Alqurashi et al., 2016; Horvat, Dobrota, Krsmanovic, \& Cudanov, 2015; Ke \& Kwak, 2013; Lan \& Sie, 2010).
-Within this framework, anxiety has been linked in several research studies (e.g., Teimouri, Goetze, \& Plonsky, 2019) as an indicator of poor linguistic development.
-Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment.
-Furthermore, Webb, Doman, and Pusey (2014) studied the attitudes of students and teachers in a flipped online classroom of Chinese.
-Their results showed an incremental fluctuation in their perception.
-That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term.
-A similar psychological development is observed in Ushida (2005) study which investigated the changes in students' attitudes and motivation over time in online language courses.
-Their results showed a similar evolution within the student's attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term.
-Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al.~2018), as well as the familiarity and complexity of the instruments that the course requires (Heckel and Ringeisen (2019)), which might involve some training and assistance before the beginning of the online course.
-During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, Tomasik, Helbling, and Moser (2021), leading to an overall feeling of less effective education Top hat (2020), Hodges, Moore, Lockee, Trust, and Bond (2020), Lee (2022).
-While the immediate transition to online education seemed rushed in Ruiz-Alonso-Bartol, Querrien, Dykstra, Fernández-Mira, and Sánchez-Gutiérrez (2022) the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting.
-Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format.
-Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments (Chakraborty, Mittal, Gupta, Yadav, \& Arora, 2021).
-The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years.
-This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education.
-With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes.
-The goal of this paper is dual, first to determine if online education is still in demand among our undergraduate students, and to identify what are the attitudes towards it in a context where online education is no longer mandatory.
-Our second goal is to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.
+\hypertarget{motivation}{%
+\paragraph{Motivation}\label{motivation}}
 
-\hypertarget{research-gap-and-theoretical-approach}{%
-\section{Research gap and theoretical approach}\label{research-gap-and-theoretical-approach}}
+With the decrease in covid cases, most major US universities are looking to transition into face-to-face settings, creating a new reality within language education.
+A global survey (Widenhorn, Hardy, Manuel, Botha, \& Robinson, 2023) of more than 5.000 university students revealed that more than four in five students (82\%) would still want to have at least some of their courses online after having passed two years of the global pandemic.
+Similarly, two in five university students (41\%) would still prefer to continue online without physical interaction with the educational classroom.
+When asked what factors other than the pandemic had an impact, students replied with the economy (73\%), location or transportation (44\%), and lack of access to technology (35\%)
+This is the most extensive study that tackles the shift toward face-to-face education after the online pandemic to date.
+However, this study is broad as it covers several countries with different economic needs and transportation necessities.
+Therefore, our study aims to provide more fine-grained detail about the post-pandemic tendencies in a North Eastern US university \ldots.
 
-Education mirrors society and its challenges, with Covid-19 as a global example of the adaptations that educators around the world had to implement in order to continue providing education to their students.
-In this sense, education can be understood as a continuum that has endlessly developed according to the socioeconomic changes that society experiences throughout history.
+\hypertarget{grounded-theory}{%
+\subsection{Grounded theory}\label{grounded-theory}}
 
-Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years.
-The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education.
-Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment.
-To better understand these tendencies, we employed the lens of The Grounded Theory, as it allows a cyclical observation of a changing world.
-The Grounded Theory considers a changing environment that can evolve, becoming the researcher a constant observer of the changes produced (Hernandez Carrera, 2014).
-Having a better understanding of the constant change of tendencies that affect our students can help us not only to provide them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.
+In order to study and understand tendencies in online learning, we turned to Grounded Theory, as it allows for a cyclical observation of a changing world, where the researcher is a constant observer of the changes produced (Hernandez Carrera, 2014).
+This theoretical approach allows the research team to explain the relationships among categories within the same reality.
+It is a constant comparison methodology of data of the reality being studied, where the hypothesis are formulated throughout the research process.
+This was performed via student evaluations, which allowed to test the thematic coding structuration and check for unanticipated topics.
+In this step, the most noteworthy categories were selected (axial coding) with the intention of making a posterior analysis (selected coding).
+A Qualtrics Survey followed this initial observation, which allowed us to employ a mixed models questionnaire that included qualitative, quantitative, and open-ended questions aimed at gaining information about the participant's experience, attitudes, and motivations for taking online vs.~in-person language classes.
+We then tested each category in\ldots{} (add statisct analysis used).
 
-This theoretical approach allowed us to perform mixed models including qualitative, quantitative, and open questionary deriving the hypothesis we present in this paper.
-This approach was chosen as it allows the researcher to observe a constant change in tendencies and derive a hypothesis based on the collected data.
-Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them (Corbin \& Strauss, 2014).
+Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within a specific area, along with the factors that affect them (Corbin \& Strauss, 2014).
+Thus we understand that the results we obtain might be limited to the area from where the information is being extracted.\\
+Social factors such as distance from campus, commuting time, working hours, or access to the internet might be geographically dependent and not extrapolable to other areas or countries.
 
@@
 \section{Current Study}\label{current-study}}
-
-Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years.
-The effects of this ever-changing learning environment have affected students and continue to affect modulating the way they interact with and view their education.
-Post-pandemic effects, along with world socio-economic changes, have brought a new educational reality that affects tendencies toward enrollment.
-Having a better understanding of the constant change of tendencies that affect our students can help us not only in providing them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-chakraborty2021opinion}{}}%
-Chakraborty, P., Mittal, P., Gupta, M.
-S., Yadav, S., \& Arora, A.
-(2021).
-Opinion of students on online education during the COVID-19 pandemic.
-\emph{Human Behavior and Emerging Technologies}, \emph{3}(3), 357--365.
-
 \leavevmode\vadjust pre{\hypertarget{ref-corbin2014basics}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-heckel2019pride}{}}%
-Heckel, C., \& Ringeisen, T.
-(2019).
-Pride and anxiety in online learning environments: Achievement emotions as mediators between learners' characteristics and learning outcomes.
-\emph{Journal of Computer Assisted Learning}, \emph{35}(5), 667--677.
+\leavevmode\vadjust pre{\hypertarget{ref-nationalstatistics_2022}{}}%
+Education Statistics, N.
+C.
+for.
+(2022).
+Coe - undergraduate enrollment - national center for education statistics.
+U.S.
+Department of Education, Institute of Education Sciences.
+Retrieved from \url{https://nces.ed.gov/programs/coe/indicator/cha}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tophatfall2020}{}}%
+Hat, T. (2021). Adrift in a pandemic: Survey of 3,089 students finds uncertainty about returning to college. Retrieved from \url{https://tophat.com/press-releases/adrift-in-a-pandemic-survey/}
 
@@
 Hernandez Carrera, R. M. (2014). La investigacion cualitativa a trav{e}s de entrevistas: Su analisis mediante la teoria fundamentada. \emph{Cuestiones Pedagogicas, 23, 187-210}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-hodges2020difference}{}}%
-Hodges, C. B., Moore, S., Lockee, B. B., Trust, T., \& Bond, M. A. (2020). \emph{The difference between emergency remote teaching and online learning}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-kebritchi2017issues}{}}%
+Kebritchi, M., Lipschuetz, A., \& Santiague, L.
+(2017).
+Issues and challenges for teaching successful online courses in higher education: A literature review.
+\emph{Journal of Educational Technology Systems}, \emph{46}(1), 4--29.
+
 \leavevmode\vadjust pre{\hypertarget{ref-lan2010using}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-lee2022factors}{}}%
-Lee, S.-M. (2022). Factors affecting the quality of online learning in a task-based college course. \emph{Foreign Language Annals}, \emph{55}(1), 116--134.
+\leavevmode\vadjust pre{\hypertarget{ref-mahyoob2020challenges}{}}%
+Mahyoob, M. (2020). Challenges of e-learning during the COVID-19 pandemic experienced by EFL learners. \emph{Arab World English Journal (AWEJ)}, \emph{11}(4).
+
+\leavevmode\vadjust pre{\hypertarget{ref-mccutcheon2015systematic}{}}%
+McCutcheon, K., Lohan, M., Traynor, M., \& Martin, D.
+(2015).
+A systematic review evaluating the impact of online or blended learning vs.
+Face-to-face learning of clinical skills in undergraduate nurse education.
+\emph{Journal of Advanced Nursing}, \emph{71}(2), 255--270.
+
+\leavevmode\vadjust pre{\hypertarget{ref-means2013effectiveness}{}}%
+Means, B., Toyama, Y., Murphy, R., \& Baki, M.
+(2013).
+The effectiveness of online and blended learning: A meta-analysis of the empirical literature.
+\emph{Teachers College Record}, \emph{115}(3), 1--47.
 
@@
 \emph{System}, \emph{104}, 102684.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sun2016online}{}}%
+Sun, A., \& Chen, X. (2016). Online education and its effective practice: A research review. \emph{Journal of Information Technology Education}, \emph{15}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ushida2005role}{}}%
-Ushida, E. (2005). The role of students' attitudes and motivation in second language learning in online language courses. \emph{CALICO Journal}, 49--78.
-
-\leavevmode\vadjust pre{\hypertarget{ref-webb2014flipping}{}}%
-Webb, M., Doman, E., \& Pusey, K. (2014). Flipping a chinese university EFL course: What students and teachers think of the model. \emph{The Journal of Asia TEFL}, \emph{11}(4), 53--87.
+\leavevmode\vadjust pre{\hypertarget{ref-widenhorn2023comparing}{}}%
+Widenhorn, M., Hardy, D.
+W., Manuel, J.
+A., Botha, A., \& Robinson, R.
+(2023).
+Comparing global university mindsets and student expectations: Closing the gap to create the ideal learner experience.
+\emph{Available at SSRN 4320170}.
 

### 2023-01-21 scripts/00_libraries.R

@@ -24,5 +24,6 @@ library("foreign")
 library("MASS")
 library("Hmisc")
 library("reshape2")
+library("tinytex")
 
 # -----------------------------------------------------------------------------

### 2023-02-01 docs/draft/draft.Rmd
cambios

@@
 
-According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses [@nationalstatistics_2022].
+According to the [@nationalstatistics_2022], during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses [@nationalstatistics_2022].
 Compared to Fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs.
@@
 <!--- for example, x, y, z helps students to do a, b, and c. then start with the next sentence--->  
-However, the Covid-19 pandemic appeared to be its hardest challenge to date, as many educators where not prepare for the online transition @tomasik2021educational.
-<!--- in what way?
+ Even though many programs already had online versions of their courses,   the Covid-19 pandemic postulated a challenge to many educators, as they were not prepared and, in some cases, lacked of experience teaching the online modality  @tomasik2021educational <!--- in what way?
 are we saying covid was a challenge for online learning?
@@
 
-The outbreak of COVID-19 has caused online teaching and learning to evolve rapidly during the past two years due to the national online swift. 
-However, with the progressive decrease in global covid cases, universities are adopting a pre-pandemic approach, making students return to the educational classroom.
-
 <!--- This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education.
 - maybe delete this --->
-With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes.
+With a global decrease in Covid-19 cases, most US universities are slowly beginning to switch to a pre-pandemic educational setting or blend hybrid classes.
 <!--- idk if we can say "global decrease" maybe something like "with a push to return to pre-covid practices" --->

### 2023-02-01 docs/draft/draft.tex
cambios

@@
 
-According to the National Center for Education Statistics (2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses (Education Statistics, 2022).
+According to the (Education Statistics, 2022), during the fall of 2020 over 75 percent of undergraduate students (11.8 million) were enrolled in at least one online course, whereas 44 percent (7.0 million) of all undergraduate students exclusively enrolled in online courses (Education Statistics, 2022).
 Compared to Fall 2019, these numbers represent a 97 percent increase in undergraduates taking at least one online course (11.8 million vs.~6.0 million) and a 186 percent increase in undergraduate students enrolled exclusively in online courses (7.0 million vs.~2.4 million).
 
-However, the Covid-19 pandemic appeared to be its hardest challenge to date, as many educators where not prepare for the online transition Tomasik, Helbling, and Moser (2021).
+Even though many programs already had online versions of their courses, the Covid-19 pandemic postulated a challenge to many educators, as they were not prepared and, in some cases, lacked of experience teaching the online modality Tomasik, Helbling, and Moser (2021)
 
-The outbreak of COVID-19 has caused online teaching and learning to evolve rapidly during the past two years due to the national online swift.
-However, with the progressive decrease in global covid cases, universities are adopting a pre-pandemic approach, making students return to the educational classroom.
-
-With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes.
+With a global decrease in Covid-19 cases, most US universities are slowly beginning to switch to a pre-pandemic educational setting or blend hybrid classes.
 The goal of this paper is twofold, first to identify attitudes towards online language education it in a context where online education is no longer mandatory and, second to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.
